---
title: "Untitled"
format: html
editor: visual
---
```{r renv}
#| eval = FALSE
renv::diagnostics()
renv:::renv_download_method()
renv::restore()
getOption("repos")
renv::restore(repos="https://cloud.r-project.org")
R.Version()$platform
R.version.string
```

```{r}
pacman::p_load(
  IBrokers, # xts objects
  broom, dplyr, stringr, janitor,
  timetk, tsibble,
  tidyverse, tidyquant, 
  PerformanceAnalytics
)
```

```{r IBrokers}
# Get short description
packageDescription("IBrokers") %>% str(list.len = 4)
# Load help page
help(package="IBrokers")
# List all datasets in "IBrokers"
data(package="IBrokers") 
# List all objects in "IBrokers"
ls("package:IBrokers") %>% head()
# See ?IBrokers for details.
# IBrokersRef()
```


```{r twsConnect}
# IBrokers version 0.9-10.  Implementing API Version 9.64
tws = twsConnect(port=7496)
isConnected(tws) %>% 
  stopifnot("no IB connection?" = .)
tws %>% twsConnectionTime()
tws %>% reqCurrentTime()
# tws %>% reqIds() # write mode ON - next available ID
tws %>% serverVersion()
# tws %>% setServerLogLevel(logLevel = 2) # 1-5
# on.exit(twsDisconnect(tws))
```

1. reqContractDetails: product information.
1. reqHistoricalData: historical data
  + https://github.com/algoquant/lecture_slides/blob/af992c5c8d2c44fd06fd5d3adf0bc5a7e229cc00/markets_trading.R#L1446
    + reqHistoricalData for multiple stocks

1. reqRealTimeBars # 5 second OHLCVWC bar
1. reqMktData: real-time market data.
  + reqMktData(tws, contract) subscription required
  + [https://blog.quantinsti.com/r-implementation-in-interactive-brokers-api]
1. reqMktDepth: real-time order book data.

twsContract: Contract object
twsEquity/twsSTK: equity Contract objects
# https://github.com/algoquant/lecture_slides/blob/af992c5c8d2c44fd06fd5d3adf0bc5a7e229cc00/markets_trading.R#L1384C1-L1401C1 for examples
twsOption/twsOPT: option Contract objects
twsFuture/twsFUT: futures Contract objects
twsFuture/twsFOP: futures options Contract objects
twsCurrency/twsCASH: currency Contract objects

```{r reqAccountUpdates, eval = FALSE}
acc <- tws %>% reqAccountUpdates() # Account Details
acc %>% str(max.level = 2, list.len = 3)
acc[[1]] %>% unlist() %>% str()
(posns <- acc %>% twsPortfolioValue())
# tws %>% twsPortfolioValue()
# tws %>% updatePortfolio
```

## LSEETF as primaryExchange?
```{r reqMatchingSymbols}
tws %>% 
  reqMatchingSymbols(pattern = c('VEUD', "VOD")[1]) -> 
  df
df %>% 
  as_tibble() %>% 
  # remove contract. from start of colnames
  rename_with(
    ~ gsub("contract.", "", .x, fixed = TRUE), 
        starts_with("contract.")) %>% 
  arrange(symbol, 
    secType, 
    primaryExchange) %>% 
  filter(primaryExchange %>% str_detect("^LSE")) %>% 
  glimpse()
df$primaryExchange %>% unique() %>% sort()
# "LSE" NASDAQ JSE  EBS
# LSEETF (3SVO, 3LVO)
# fundamentalData(tws, contract)
```

```{r crypto}
btcusd <- twsCurrency(symbol = "ETH", currency = "USD", exch = "IDEALPRO")
# Request historical data for the last 10 days with 1 hour bars
hist.data <- reqHistoricalData(tws, 
  Contract = btcusd, 
  barSize = "1 day", 
  duration = "5 D")

# https://interactivebrokers.github.io/tws-api/basic_contracts.html#crypto
tickers <- c('SOL', 'SPY', "ETH")[3]
contract <- twsEquity(
  # conId = 0,
  symbol = tickers, 
  # sectype = 'CRYPTO',
  exch = 'PAXOS',
  primary = "",
  currency = 'USD') 
is.twsContract(contract)
details <- reqContractDetails(tws, contract)[[1]]
```

```{r twsEquity, eval = FALSE}
tickers <- c('VOD', 'SPY', "AAPL")[1]
contract <- twsEquity(tickers, 'SMART') # twsSTK
is.twsContract(contract)
as.twsContract(contract)
```

```{r reqContractDetails, eval = FALSE}
details <- reqContractDetails(tws, contract)[[1]]
as.twsContract(details)
str(details, max.level = 2, list.len = 3)
details$longName
details$exch %>% unique() %>% sort()
details$exch %>% unique() %>% sort()
details$validExchanges %>% unique() %>% sort()
# "LTSE"
```

```{r twsEquity non-USD}
# ?twsEquity currency = 'USD' is the default
contract2 <- twsEquity(
  symbol = 'VEUD', 
  # exch = 'SMART',
  primary = c('NASDAQ', 'LSE', 'LSEETF')[2]
  # , currency='EUR'
)
reqHistoricalData(tws, Contract=contract2)
contract2 <- twsEquity(
  symbol = 'VOD', primary = 'LSE', currency='GBP') 
reqHistoricalData(tws, Contract=contract2)
# https://github.com/algoquant/lecture_slides/blob/af992c5c8d2c44fd06fd5d3adf0bc5a7e229cc00/markets_trading.R#L1446

contract3 <- twsEquity(
  symbol = 'SBIN', exch = 'NSE', currency='INR') 
reqHistoricalData(tws, Contract = contract3)
```


```{r real time, eval = FALSE}
contract5 <- twsEquity('aapl', 'smart')
reqMktData(tws, Contract=contract5)
reqMktData(tws, twsEquity("QQQ"))
# Delayed market data is available.
#   VOD NASDAQ.NMS/TOP/ALL
# TODO: See link in 'Market Data Connections' dialog?
contract4 <- twsEquity(
  symbol = 'VOD', exch = 'NASDAQ', currency='USD') 
reqMktData(tws, Contract=contract4)
# subscription for LSE 
# reqMktData(tws, contract, snapshot = TRUE)
reqMktDepth(tws, contract)
reqRealTimeBars(tws, contract)
# updateMktDepth
```

### reqHistoricalData
+ only specific combinations of barSize / duration  valid
  + https://interactivebrokers.github.io/tws-api/historical_bars.html#hd_duration
  + https://interactivebrokers.github.io/tws-api/historical_limitations.html
+ some security types have no historical data 
```{r IBrokers::reqHistoricalData}
tws %>% 
  IBrokers::reqHistoricalData(
    Contract = contract,
    endDateTime = "",
    barSize = c("1 day", "1 min")[1],
    duration = c("1 Y", "1 D")[1]
    #, endDateTime = tws %>% reqCurrentTime()
    # , timeFormat, tzone
  ) %>% 
  I() ->
  dat_raw
dat_raw %>% str()
```

```{r broom yearweek}
dat_raw %>% broom::tidy() %>% glimpse()
dat_raw %>% names()
dat_raw %>% 
  # FIXME: keep the symbol name?
  to.weekly(indexAt = "last") %>% names()
  # na.omit() 
#dat_raw %>% 
  # timetk:: tk_tbl(   # from xts to tibble 
  #  preserve_index = TRUE, rename_index = "date") %>%
  # date becomes character so no longer index?
  # utils::type.convert(as.is = TRUE) %>% 
dat_raw %>% 
  broom::tidy() %>% # from xts to tibble
  separate(
    col = series, 
    into = c("symbol", "type")) %>% 
  mutate(type = type %>% tolower()) %>% 
  filter(
    type %>% 
    str_detect("high|low|open|gaps$") %>% 
    `!`) %>% # exclusions
  pivot_wider(names_from = "type") %>% 
  # aggregate == xts::to.weekly(indexAt = "last")
  mutate(time_step = yearweek(index)) %>% 
  group_by(time_step, symbol) %>% 
  summarise(
    close = last(close),
    wap   = mean(wap),
    count = sum(count),
    volume  = sum(volume),
    .groups = 'drop'
  ) %>% 
  # Return.calculate(method = "log") %>% 
  mutate(
    log_close = log(close),
    ret_close = log_close - lag(log_close, 1),
  ) %>% 
  select(-c(log_close)) %>% 
  # readr::type_convert(guess_integer = TRUE)
  # tsibble(index = "time_step", ley = 'symbol') %>% 
  I() ->
  df
str(df)
```

+ strictly enforced 10 seconds between request pacing rule implemented by the TWS
  + reqHistoricalData currently does not manage this!
  + but reqHistory does

+ reqHistory is slow IBrokers only call
  + for one year? or 5 D of 1 minute bars
  + or 10 D of 15 minute bars
  + respecting IB timeouts (10 seconds) 
    + maximum bars per request (2000)

```{r slow 1 or 15 min reqHistory, eval = FALSE}
# reqHistory request maximal history given bar size
# WARNING: only barSize == 1 min / 5 D | 15 mins / 10 D
system.time(
  tws %>% 
  IBrokers::reqHistory(
    Contract = contract,
    barSize = c("15 mins", "1 day", "1 min")[2],
    # duration = '1 D'
    #, endDateTime = tws %>% reqCurrentTime()
  ) %>% 
  I() ->
  dat_raw_hf
)
```


## plot
+ https://github.com/algoquant/lecture_slides/blob/af992c5c8d2c44fd06fd5d3adf0bc5a7e229cc00/markets_trading.R#L1578C1-L1581C1
```{r Plot OHLC, eval = FALSE}
library(dygraphs)
dygraphs::dygraph(pricev[, 1:4], main="S&P500 ESM9 futures") %>%
  dyCandlestick()
```


```{r reqHistoricalData v reqHistory, eval = FALSE}
# tws <- twsConnect()
# requested exchange == default / smart
# primary exchange == island
contract <- twsEquity('QQQ','SMART','ISLAND')

# 30 days of daily - default
Sys.sleep(10) 
reqHistoricalData(tws, Contract=contract)
# mandatory 10s - else IB pacing violation
Sys.sleep(10) 
# WARNING: slooow - default 1 year of 1 minute bars
reqHistory(tws, Contract=contract,
  barSize = c("1 day", "1 min")[1]
  # endDateTime = Sys.time()
  # duration = c("1 Y", "1 D")[2]
)

```

```{r futures}
# https://www.rpubs.com/julian_antonio/implavo_research
# Define contract 
ohlc_daily_spx = twsIND("SPX", "CBOE")
# ohlc of price and the iv 
Sys.sleep(10) 
ohlc_daily_iv_spx_IB <- reqHistoricalData(
  tws, 
  ohlc_daily_spx, 
  barSize = "1 day", 
  duration = '2 Y', 
  whatToShow = "OPTION_IMPLIED_VOLATILITY")
Sys.sleep(10) 
ohlc_daily_price_spx_IB = reqHistoricalData(tws, ohlc_daily_spx, barSize = "1 day", duration = '15 Y', whatToShow = "TRADES")

```
```{r}
# https://interactivebrokers.github.io/tws-api/basic_contracts.html#Indexes
# Contract contract = new Contract();
# contract.Symbol = "DAX";
# contract.SecType = "IND";
# contract.Currency = "EUR";
# contract.Exchange = "EUREX";

```




```{r currency, eval = FALSE}
library(twsInstrument)
contract6 <- getContract("EUR.USD")
reqHistoricalData( tws, contract6, verbose=T, whatToShow="BID" )
reqHistoricalData( tws, contract6, verbose=T, whatToShow="ASK" )

```

```{r quantmod::getQuote, eval = FALSE}
library(quantmod)
from <- c("CAD", "JPY", "USD")
to <- c("USD", "USD", "EUR")
getQuote(paste0(from, to, "=X"))
```


# https://stackoverflow.com/questions/26694042/how-to-get-currency-exchange-rates-in-r

# TODOs 
+ https://interactivebrokers.github.io/tws-api/news.html#news_providers
  + reqNewsProviders
+ https://interactivebrokers.github.io/tws-api/market_scanners.html#scanner_examples
  + ScannerSubscription
+ https://interactivebrokers.github.io/tws-api/head_timestamp.html#reqHeadTimeStamp
  + reqHeadTimeStamp
+ https://stackoverflow.com/questions/tagged/ibrokers
+ # Download raw data for multiple contracts for replay
  + https://github.com/algoquant/lecture_slides/blob/af992c5c8d2c44fd06fd5d3adf0bc5a7e229cc00/markets_trading.R#L1791
+ https://alphaarchitect.com/2024/01/equally-weighted-portfolios/
+ combined two exclusion strategies 
  + filtered stocks 
    + lowest sharpe ratios
      + five year look-back period
+ fund families 
  + Alpha Architect, AQR, Avantis, Bridgeway, and Dimensional
+ construction rules based on empirical research

## universes

+ excluding stocks with 
  + negative momentum 
  + lottery stocks 
    - high betas 
    - low profitability
    ) from their eligible 

# TODOs
+ twsInstrument
```{r}
# Install the package twsInstrument
install.packages("twsInstrument", repos="http://r-forge.r-project.org")
```

+ https://github.com/algoquant/IBrokers2
  + additional trade execution capabilities, for running systematic trading strategies in a callback loop
  + https://github.com/algoquant/IBrokers2/tree/master/vignettes
  + https://github.com/algoquant/IBrokers2/tree/master/scripts

+ https://github.com/censix/datafeedMKT-pub
+ https://github.com/censix/INTRADAY-PartAB
+ https://www.youtube.com/watch?v=zNQY5Krv8aA
  + Option Algorithmic Trading with Interactive Brokers | R
  + twsComboLeg / twsBAG
  + https://github.com/jgQuantScripts/Options-Algo

```{r twsDisconnect}
twsDisconnect(tws)
```

